A meta-analysis of mental rotation ability in the first years of life

### 2022-04-27 code/analysis.Rmd
Revert HPDIs in regression plot to fill

# Regression plot
dat_reg %>%
  ggplot(aes(x = age * 12, y = gi)) +
  geom_hline(yintercept = 0, linetype = "dashed") +

  # Regression lines and HPDIs - Habituation tasks
  stat_lineribbon(
    aes(y = .epred, color = gender_task),
    data = draws_reg,
    alpha = .4,
    point_interval = "mean_hdi"
  ) +
  # Individual study effect sizes - Habituation tasks
  geom_point(aes(color = gender_task, size = ni), shape = 0) +
  scale_color_manual(
    values = habi_colors,
    breaks = names(habi_colors),
    labels = c("Females", "Males", "Mixed gender"),
    na.value = NA
  ) +
  guides(color = guide_legend(
    title = "Habituation tasks",
    override.aes = list(fill = NA),
    order = 1
  )) +

  # Regression lines and HPDIs - VoE tasks
  ggnewscale::new_scale_color() +
  stat_lineribbon(
    aes(y = .epred, color = gender_task),
    data = draws_reg,
    alpha = .4,
    fill = NA,
    point_interval = "mean_hdi"
  ) +
  # Individual study effect sizes - VoE tasks
  geom_point(aes(color = gender_task, size = ni), shape = 0) +
  scale_color_manual(
    values = voe_colors,
    breaks = names(voe_colors),
    labels = c("Mixed gender"),
    na.value = NA
  ) +
  guides(
    color = guide_legend(
      title = "Violation of\nexpectation tasks"
    ),
    order = 2
  ) +

  # Styling
  coord_cartesian(expand = FALSE) +
  scale_x_continuous(limits = c(2.9, 16.1), breaks = seq(3, 16, 1)) +
  scale_y_continuous(limits = c(-1.2, 2.2), breaks = seq(-1, 2, 0.5)) +
  scale_fill_grey(
    start = 0.9, end = 0.7,
    labels = as_mapper(~ scales::percent(as.numeric(.x)))
  ) +
  labs(
    x = "Age (months)",
    y = expression("Hedges'" ~ italic("g")),
    fill = "Bayesian HPDI",
    size = "Sample size"
  ) +
  theme_bw() +
  theme(
    legend.key = element_blank(),
    panel.border = element_rect(size = 1),
    panel.grid = element_blank(), # element_line(color = "grey90"),
    text = element_text(family = "Helvetica"),
  )

# Save the plot
ggsave(here(figures_dir, "regression.pdf"), width = 8, height = 5)
```

>>>>

# Regression plot
dat_reg %>%
  ggplot(aes(x = age * 12, y = gi)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  # Regression lines and HPDIs - Habituation tasks
  stat_lineribbon(
    aes(y = .epred, color = gender_task),
    data = draws_reg,
    alpha = .4,
    point_interval = "mean_hdi"
  ) +
  # Individual study effect sizes - Habituation tasks
  geom_point(aes(color = gender_task, size = ni), shape = 0) +
  scale_color_manual(
    values = habi_colors,
    breaks = names(habi_colors),
    labels = c("Females", "Males", "Mixed gender"),
    na.value = NA
  ) +
  guides(color = guide_legend(
    title = "Habituation tasks",
    override.aes = list(fill = NA),
    order = 1
  )) +
  # Regression lines and HPDIs - VoE tasks
  ggnewscale::new_scale_color() +
  stat_lineribbon(
    aes(y = .epred, color = gender_task),
    data = draws_reg,
    alpha = .4,
    fill = NA,
    point_interval = "mean_hdi"
  ) +
  # Individual study effect sizes - VoE tasks
  geom_point(aes(color = gender_task, size = ni), shape = 0) +
  scale_color_manual(
    values = voe_colors,
    breaks = names(voe_colors),
    labels = c("Mixed gender"),
    na.value = NA
  ) +
  guides(
    color = guide_legend(
      title = "Violation of\nexpectation tasks"
    ),
    order = 2
  ) +
  # Styling
  coord_cartesian(expand = FALSE) +
  scale_x_continuous(limits = c(2.9, 16.1), breaks = seq(3, 16, 1)) +
  scale_y_continuous(limits = c(-1.2, 2.2), breaks = seq(-1, 2, 0.5)) +
  scale_fill_grey(
    start = 0.9, end = 0.7,
    labels = as_mapper(~ scales::percent(as.numeric(.x)))
  ) +
  labs(
    x = "Age (months)",
    y = expression("Hedges'" ~ italic("g")),
    fill = "Bayesian HPDI",
    size = "Sample size"
  ) +
  theme_bw() +
  theme(
    legend.direction = "vertical",
    legend.key = element_blank(),
    legend.position = "none",
    panel.border = element_rect(size = 1),
    panel.grid = element_blank(), # element_line(color = "grey90"),
    text = element_text(family = "Helvetica"),
  ) -> plot_reg

# Extract the legend so that we can put it inside the plotting area
plot_reg_legend <- get_legend(plot_reg + theme(legend.position = "top"))

# Plot posterior distributions of the regression coefficients
draws_reg_coef <- tidy_draws(res_brm_reg)
draws_reg_coef %>%
  select(coef_colnames) %>%
  gather() %>%
  mutate(coef = factor(key, levels = names(coef_colnames))) %>%
  ggplot(aes(x = value, y = fct_rev(coef))) +
  geom_vline(xintercept = 0) +
  stat_halfeye(point_interval = mean_hdi) +
  coord_cartesian(xlim = c(-1.25, 1.25)) +
  scale_x_continuous(breaks = seq(-1, 1, 0.5)) +
  labs(
    x = expression("Regression weight (" * Delta * italic("g") * ")"),
    y = NULL
  ) +
  theme_bw() +
  theme(
    panel.grid = element_blank(),
    axis.text.y = element_text(hjust = 1),
    panel.border = element_rect(size = 1)
  ) -> plot_coef

# Combine plots
plot_grid(
  plot_reg, plot_coef,
  nrow = 1, rel_widths = c(3, 2), labels = "AUTO"
) +
  draw_plot(plot_reg_legend, x = 0.37, y = 0.84, hjust = 0.5, vjust = 0.5)

# Save plot
ggsave(here(figures_dir, "regression_coef.pdf"), width = 12, height = 5)
```
